Paper Analysis

### 2024-10-17 Paper_WriteUp/Paper_Plots.qmd
trying to tidy all of this up

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(ggridges)
library(here)
library(viridis)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

@@

```{r summary statistics 1700-1900}

path_id <- 1  ## for 1700-1900

data_path <- all_data_path[path_id]

files <- list.files(data_path)

@@

## for each player, count how many times they start
## a game with 3 minutes of the start of a previous game
## and get the proportion across all focal players
 bullet_data |>  
   group_by(Username) |> 
   select(Username, UTCDate, UTCTime) |> 
   mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
   group_by(Username) |> 
   arrange(date_time) |> 
   mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
   mutate(less_3 = ifelse(gap_seconds <= 180, TRUE, FALSE)) |> 
   ungroup() |>   ## to get the overall proportion
   summarise(sum(less_3, na.rm = TRUE)/ n())

@@

## repeat for blitz games

outcomes_blitz <- blitz_data |> 
  # group_by(Username) |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_7 = if_else(gap_seconds <= 420, TRUE, FALSE, missing = FALSE))

@@

result_blitz |> 
  unnest_longer(session_length) |> 
  mutate(multiple = if_else(session_length > 1, TRUE, FALSE)) |>  
  summarise(sum(multiple)/n())

```{r summary statistics gm}
## then repeat this analysis for the gms
path_id <- 4  ## for GMs
data_path <- all_data_path[path_id]
files <- list.files(data_path)

lichess_data_gm <- files |> 
  map_dfr(~read_player(data_path, .x))

@@

## look at the proportion of games started within 3 minutes 
## of the previous game
bullet_data_gm |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_3 = ifelse(gap_seconds <= 180, TRUE, FALSE)) |> 
  ungroup() |>   ## to get the overall proportion
  summarise(sum(less_3, na.rm = TRUE)/ n())

## look at the streaks, number of games played in a session
outcomes_gm <- bullet_data_gm |> 
  # group_by(Username) |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_3 = if_else(gap_seconds <= 180, TRUE, FALSE, missing = FALSE))

@@

# Apply function to each group
result_gm <- outcomes_gm |> 
  summarise(session_length = list(get_true_sequences(less_3)))

@@

@@

```{r plot global parameters for 17-19}
data_path <- here("results/lichess1700-1900")

@@

```{r interpret the estimated coefficients 17-19}

gamma_ests <- fit_17_19_bullet_prev$summary(variables = c("gamma1",
                                                          "gamma2")) |> 
  pull(mean)
## compute change in win probability for gamma1
1/(1 + exp(-1 * (0)))
1/(1 + exp(-1 * (gamma_ests[1])))

1/(1 + exp(-1 * (0))) ## equally rated, playing as black
1/(1 + exp(-1 * (100 * gamma_ests[2])))

@@

```{r player level parameters for 17-19}

## need to get the write names then for these parameters here
## did this somewhere before already

player_id <- as_tibble(bullet_17_19) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

## then the winner effects plot
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~player_name, scales = "free", ncol = 6) +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

winner_plot_17_19

## then repeat for player effects

indiv_plot_17_19 <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~player_name, scales = "free", ncol = 6) +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

indiv_plot_17_19

ggsave(plot = indiv_plot_17_19, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "17_19_prev_indiv.png")), dpi = 600,
       height = 7, width = 7)

@@

```{r new boxplots}

winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated W/L-Effect", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

ggsave(plot = indiv_plot_17_19, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "17_19_prev_indiv.png")), dpi = 600,
       height = 7, width = 7)

@@

```{r global parameters for gm data}
data_path <- here("results/lichessGrandmasters")

@@

ggsave(plot = global_gm_bullet_prev, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_prev_global.png")), dpi = 600,
       height = 5, width = 7)

```{r interpret the estimated coefficients gm}

gamma_ests_gm <- fit_gm_bullet_prev$summary(variables = c("gamma1",
                                                          "gamma2")) |> 
  pull(mean)

## compute change in win probability for gamma1
1/(1 + exp(-1 * (0)))
1/(1 + exp(-1 * (gamma_ests_gm[1])))

## change in win probability for elo difference

1/(1 + exp(-1 * (0))) ## equally rated, playing as black
1/(1 + exp(-1 * (100 * gamma_ests_gm[2])))

@@

```{r player level parameters for gm data}
player_id <- as_tibble(bullet_gm) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

## then repeat for player effects

indiv_plot_gm <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

ggsave(plot = indiv_plot_gm, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_prev_indiv.png")), dpi = 600,
       height = 7, width = 7)

```{r interpret changes in win probability for gm}
## interpret the individual winner effects
## assume wins 50% of all games

1/(1 + exp(-1 * (0)))

## if won previous
1/(1 + exp(-1 * (0 + 0.216 * 0.5)))

## if lost previous
1/(1 + exp(-1 * (0 + 0.216 * - 0.5)))

## what about if win probability overall was 40%
1/(1 + exp(-1 * (0 + 0.216 * 0.6)))

## 35%, pretty low
1/(1 + exp(-1 * (0 + 0.216 * 0.65)))

@@

```{r compare global params n-1 vs n-10}
## global effects first
data_path <- here("results/lichessGrandmasters")

fit_gm_bullet_10 <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model.RDS"))

@@

## then compare the winner effects and individual effects. 
## will just show for the first 6 players for convenience

player_pars_pre <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Prev. Game")

@@

## then player effects
## should update this also
hist_comp_player <- bind_rows(player_pars_pre, player_pars_pre_10) |> 
  filter(id < 7) |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

hist_comp_player

ggsave(plot = hist_comp_player, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_comp_player.png")), dpi = 600,
       height = 5, width = 7)

<!-- down to here in terms of updating the code, making sure it's complete -->

@@

```{r bullet v blitz for 17-19}
data_path <- here("results/lichess1700-1900")

fit_17_19_blitz_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_blitz_model_prev.RDS"))

blitz_17_19 <- readRDS(file = paste0(data_path, "/users_blitz.RDS"))

## compare global effects first

bullet_pars <- fit_17_19_bullet_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  mutate(model = "Bullet")

@@

ggsave(plot = comp_17_19_player, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_17_19_player.png")), dpi = 600,
       height = 5, width = 7)

@@

```{r bullet v blitz gm}
data_path <- here("results/lichessGrandmasters")

@@

## then repeat for winner and player effects

player_pars_bullet <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

@@

ggsave(plot = comp_gm_winner, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_winner.png")), dpi = 600,
       height = 5, width = 7)

@@

ggsave(plot = comp_gm_player, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_player.png")), dpi = 600,
       height = 5, width = 7)

@@

```{r ppc 17-19}
## this the global and winner effect plots
path_id <- 1
data_path <- res_data_path[path_id]

@@

```{r ppc1 for 17-19}
path_id <- 1
data_path <- res_data_path[path_id]

@@

```{r ppc2 for 17-19}
## time varying ppc for 1700-1900 players
draws <- fit_17_19_first$draws() |> as_draws_df() |>
  select(starts_with(c("beta[", "gamma"))) |>
  mutate(draw = row_number()) |> 
  pivot_longer(cols = "beta[1,1]":"beta[2,10]") |> 
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  select(-name) |> 
  pivot_wider(names_from = param, values_from = value) |> 
  rename(beta1 = `1`, beta2 = `2`)

@@

```{r perm for 17-19}
perm_data_path <- here("results/lichess1700-1900/perm")

@@

```{r perm winner effects}
## get the selected users for this, top 20 players
path_id <- 1  ## for 1700-1900
data_path <- all_data_path[path_id]
files <- list.files(data_path)

@@

```{r ppc1 and ppc2 for gm}
## just do ppc plots for now
path_id <- 4
data_path <- res_data_path[path_id]
fit_gm_first <- readRDS(file =  here(data_path, "time",
                                        "select_users_first_bullet.RDS"))
fit_gm_last <- readRDS(file =  here(data_path, "time",
                                        "select_users_last_bullet.RDS"))

@@

```{r}
perm_data_path <- here("results/lichessGrandmasters/perm/")

@@

```{r}

@@

```{r}

data_path <- here("results/lichess2000-2200")

@@

```{r}

data_path <- here("results/lichess2300-2500")

@@

What about for the other two groups?

__To be added in__

![Time-Varying PPC for 2000-2200](../results/lichess2000-2200/time/ppc_fit_first_last_bullet.png)

![Time-Varying PPC for 2300-2500](../results/lichess2300-2500/time/ppc_fit_first_last_bullet.png)

Maybe some very limited evidence that this becomes less
reasonable for players with a higher rating.

>>>>

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(ggridges)
library(here)
library(ggdist)
library(viridis)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

@@

```{r summary statistics 1700-1900}
#| eval: false
## this can be run if interested
path_id <- 1  ## for 1700-1900 
data_path <- all_data_path[path_id]
files <- list.files(data_path)
lichess_data <- files |> 
  map_dfr(~read_player(data_path, .x))

@@

## for each player, count how many times they start
## a game with 5 minutes of the start of a previous game
## and get the proportion across all focal players
 bullet_data |>  
   group_by(Username) |> 
   select(Username, UTCDate, UTCTime) |> 
   mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
   group_by(Username) |> 
   arrange(date_time) |> 
   mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
   mutate(less_5 = ifelse(gap_seconds <= 300, TRUE, FALSE)) |> 
   ungroup() |>   ## to get the overall proportion
   summarise(sum(less_5, na.rm = TRUE)/ n())

@@

## repeat for blitz games
outcomes_blitz <- blitz_data |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_7 = if_else(gap_seconds <= 420, TRUE, FALSE, missing = FALSE))

@@

result_blitz |> 
  unnest_longer(session_length) |> 
  mutate(multiple = if_else(session_length > 1, TRUE, FALSE)) |>  
  summarise(sum(multiple)/n())
```

```{r summary statistics gm}
#| eval: false
## can be run if interested
## then repeat this analysis for the gms
path_id <- 4  ## for GMs
data_path <- all_data_path[path_id]
files <- list.files(data_path)
lichess_data_gm <- files |> 
  map_dfr(~read_player(data_path, .x))

@@

## look at the proportion of games started within 5 minutes 
## of the previous game
bullet_data_gm |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_5 = ifelse(gap_seconds <= 300, TRUE, FALSE)) |> 
  ungroup() |>   ## to get the overall proportion
  summarise(sum(less_5, na.rm = TRUE)/ n())

## look at the streaks, number of games played in a session
outcomes_gm <- bullet_data_gm |> 
  # group_by(Username) |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_5 = if_else(gap_seconds <= 300, TRUE, FALSE, missing = FALSE))

@@

# Apply function to each group
result_gm <- outcomes_gm |> 
  summarise(session_length = list(get_true_sequences(less_5)))

@@

```{r figure 1}

## to be added

```{r figure 2}

@@

```{r figure 3 - plot global parameters for 17-19}
data_path <- here("results/lichess1700-1900")

@@

```{r interpret the estimated coefficients 17-19}
#| eval: false
gamma_ests <- fit_17_19_bullet_prev$summary(variables = 
                                              c("gamma1",
                                                "gamma2")) |> 
  pull(mean)
## compute change in win probability for gamma1
1/(1 + exp(-1 * (0)))
1/(1 + exp(-1 * (gamma_ests[1])))

1/(1 + exp(-1 * (0))) ## equally rated, playing as black
1/(1 + exp(-1 * (100 * gamma_ests[2])))
```

@@

```{r player level parameters for 17-19}
player_id <- as_tibble(bullet_17_19) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

@@

```{r figure 4 left}
winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated W/L-Effect", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

ggsave(plot = indiv_plot_17_19, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "17_19_prev_indiv.png")), dpi = 600,
       height = 7, width = 7)
```

@@

```{r figure 3 - global parameters for gm data}
data_path <- here("results/lichessGrandmasters")

@@

ggsave(plot = global_gm_bullet_prev, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_prev_global.png")), dpi = 600,
       height = 5, width = 7)
```

```{r interpret the estimated coefficients gm}
#| eval: false
gamma_ests_gm <- fit_gm_bullet_prev$summary(variables = c("gamma1",
                                                          "gamma2")) |> 
  pull(mean)
## compute change in win probability for gamma1
1/(1 + exp(-1 * (0)))
1/(1 + exp(-1 * (gamma_ests_gm[1])))

## change in win probability for elo difference
1/(1 + exp(-1 * (0))) ## equally rated, playing as black
1/(1 + exp(-1 * (100 * gamma_ests_gm[2])))

@@

```{r figure 4 right - player level parameters for gm data}
player_id <- as_tibble(bullet_gm) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

## then repeat for player effects
indiv_plot_gm <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

ggsave(plot = indiv_plot_gm, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_prev_indiv.png")), dpi = 600,
       height = 7, width = 7)
```

```{r interpret changes in win probability for gm}
#| eval: false
## interpret the individual winner effects
## assume wins 50% of all games
1/(1 + exp(-1 * (0)))
## if won previous
1/(1 + exp(-1 * (0 + 0.216 * 0.5)))
## if lost previous
1/(1 + exp(-1 * (0 + 0.216 * - 0.5)))
## what about if win probability overall was 40%
1/(1 + exp(-1 * (0 + 0.216 * 0.6)))
## 35%, pretty low
1/(1 + exp(-1 * (0 + 0.216 * 0.65)))
```

@@

```{r figure 5 - compare global params n-1 vs n-10}
## global effects first
data_path <- here("results/lichessGrandmasters")
fit_gm_bullet_10 <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model.RDS"))

@@

```{r}
#| eval: false
## TO DO - move to supplement
## not required for a paper plot
player_pars_pre <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Prev. Game")

@@

## then player effects
## should update this also
hist_comp_player <- player_pars_pre |> 
  filter(param == 1) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_pre_10 |> filter(param == 1) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = position_dodge(width = 1)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

hist_comp_player
ggsave(plot = hist_comp_player, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_comp_player.png")), dpi = 600,
       height = 5, width = 7)
```

@@

```{r bullet v blitz for 17-19}
#| eval: false

## TO DO - not a current paper plot, not updated
data_path <- here("results/lichess1700-1900")
fit_17_19_bullet_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_bullet_model_prev.RDS"))
bullet_17_19 <- readRDS(file = paste0(data_path, "/users_bullet.RDS"))
fit_17_19_blitz_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_blitz_model_prev.RDS"))
blitz_17_19 <- readRDS(file = paste0(data_path, "/users_blitz.RDS"))

## compare global effects first
bullet_pars <- fit_17_19_bullet_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  mutate(model = "Bullet")

@@

ggsave(plot = comp_17_19_player, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_17_19_player.png")), dpi = 600,
       height = 5, width = 7)
```

@@

```{r figure 5 - bullet v blitz gm}
data_path <- here("results/lichessGrandmasters")

@@

## then repeat for winner and player effects
player_pars_bullet <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

@@

ggsave(plot = comp_gm_winner, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_winner.png")), dpi = 600,
       height = 5, width = 7)
```

```{r}
#| eval: false

@@

ggsave(plot = comp_gm_player, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_player.png")), dpi = 600,
       height = 5, width = 7)
```

<!-- TO DO - Update Below here -->
<!-- Everything down as far as here up to date. -->
<!-- setting everything below to eval: false for now -->

@@

```{r ppc 17-19}
#| eval: false
## this the global and winner effect plots
path_id <- 1
data_path <- res_data_path[path_id]

@@

```{r ppc1 for 17-19}
#| eval: false
path_id <- 1
data_path <- res_data_path[path_id]

@@

```{r ppc2 for 17-19}
#| eval: false
## time varying ppc for 1700-1900 players
draws <- fit_17_19_first$draws() |> as_draws_df() |>
  select(starts_with(c("beta[", "gamma"))) |>
  mutate(draw = row_number()) |> 
  pivot_longer(cols = "beta[1,1]":"beta[2,10]") |> 
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  select(-name) |> 
  pivot_wider(names_from = param, values_from = value) |> 
  rename(beta1 = `1`, beta2 = `2`)

@@

```{r perm for 17-19}
#| eval: false
perm_data_path <- here("results/lichess1700-1900/perm")

@@

```{r perm winner effects}
#| eval: false
## get the selected users for this, top 20 players
path_id <- 1  ## for 1700-1900
data_path <- all_data_path[path_id]
files <- list.files(data_path)

@@

```{r ppc1 and ppc2 for gm}
#| eval: false
## just do ppc plots for now
path_id <- 4
data_path <- res_data_path[path_id]
fit_gm_first <- readRDS(file =  here(data_path, "time",
                                        "select_users_first_bullet.RDS"))
fit_gm_last <- readRDS(file =  here(data_path, "time",
                                        "select_users_last_bullet.RDS"))

@@

```{r}
#| eval: false
perm_data_path <- here("results/lichessGrandmasters/perm/")

@@

```{r}
#| eval: false

@@

```{r}
#| eval: false
data_path <- here("results/lichess2000-2200")

@@

```{r}
#| eval: false
data_path <- here("results/lichess2300-2500")

@@

<!-- What about for the other two groups? -->

<!-- __To be added in__ -->

<!-- ![Time-Varying PPC for 2000-2200](../results/lichess2000-2200/time/ppc_fit_first_last_bullet.png) -->

<!-- ![Time-Varying PPC for 2300-2500](../results/lichess2300-2500/time/ppc_fit_first_last_bullet.png) -->

<!-- Maybe some very limited evidence that this becomes less -->
<!-- reasonable for players with a higher rating. -->
